\subsection{Stakeholders, Roles, and Expectations}
\subsubsection{Stakeholders}
Stakeholders are individuals or entities who can affect or are affected by the project outcomes.\\[4pt]
\textbf{Primary:} HCMUT staff (customer), course instructors (project managers), development team, designers.\\
\textbf{Secondary:} Students (end-users), tutors, government, competitors.

Stakeholders may be internal (within HCMUT: Office of Academic Affairs, Office of Student Affairs, departments) or external (students, tutors).

\subsubsection{Roles}
Roles are permissions and capabilities within the system: Student, Tutor, Coordinator, Department Chair, Program Administrator.

\subsubsection{Expectations}
Each role expects secure access, clear workflows, and reliable performance. Students expect easy registration and booking; tutors expect manageable scheduling; administrators expect robust reporting.

\subsection{Objectives and Scope}
\paragraph{Objectives} Design and develop an efficient, secure, and scalable software supporting the Tutor/Mentor program:
\begin{itemize}
  \item Manage tutor/student information (profiles, expertise, support needs).
  \item Enable registration, selection or automated matching.
  \item Support scheduling, booking, cancellation, rescheduling (online or in-person).
  \item Provide progress tracking, feedback, evaluation.
  \item Generate reports for departments and offices to optimize resources and recognition.
  \item Integrate with HCMUT SSO/DataCore/Library for consistency and security.
\end{itemize}

\paragraph{Scope} This specification covers:
\begin{itemize}
  \item Core features: profile management, matching, scheduling, notifications, feedback, reporting.
  \item Integrations: HCMUT\_SSO (auth), HCMUT\_DATACORE (personal data), HCMUT\_LIBRARY (learning resources).
  \item Roles: Student, Tutor, Coordinator, Department Chair, Program Admin (RBAC).
\end{itemize}
\textbf{Out of Scope (MVP)}: Full production DB, advanced AI features (smart matching, personalization), external integrations beyond HCMUT.
