
In accordance with the project guidelines on responsible Generative AI usage, our team adopted AI tools in a controlled, transparent, and academically ethical manner. The use of AI was limited to supporting activities where it provided efficiency gains without replacing core technical understanding or deliverable creation.

\subsection*{Scope of AI Usage}
Generative AI was employed strictly for auxiliary purposes, including:
\begin{itemize}
    \item \textbf{Summarization and clarification of project materials:} AI was used to condense long requirement descriptions, meeting notes, and reference documents to support faster team coordination.
    \item \textbf{Idea exploration and conceptual outlining:} During requirement analysis and early design phases, AI assisted in generating preliminary ideas or alternative approaches, which were then fully validated and rewritten by team members.
    \item \textbf{Debugging assistance:} AI was used to interpret error messages, analyze logs, and propose potential debugging steps. All code fixes and final implementations were made manually based on our own evaluation.
\end{itemize}

\subsection*{Activities Where AI Was Not Used}
To preserve authenticity and comply with the project requirements, AI was \textbf{not} used for any core technical work, including:
\begin{itemize}
    \item Writing functional or non-functional requirements.
    \item Developing use-case descriptions or scenarios.
    \item Constructing system architecture, deployment views, or development views.
    \item Creating UML diagrams (sequence, activity, class, or state-chart diagrams).
    \item Implementing source code, data models, business logic, or algorithms.
    \item Designing mockups, UI flows, or system interactions.
\end{itemize}

All of these components were manually developed by team members through independent analysis, team discussion, and iterative refinement.

\subsection*{Rationale for Limited AI Use}
This approach ensures that:
\begin{itemize}
    \item All technical deliverables reflect genuine understanding and original work.
    \item AI is used only where it meaningfully reduces administrative or repetitive workload.
    \item The project complies fully with academic integrity guidelines by avoiding over-reliance on automated tools.
\end{itemize}

\subsection*{Transparency and Integrity}
The above description represents the complete and accurate disclosure of AI usage throughout the project. No unreported, excessive, or concealed use of Generative AI occurred. All substantial technical outputs were created directly by the team, consistent with the academic integrity requirements stated in the project description.
